\mytitle{}

### 2019-07-31 paper/infocom.tex
Finalest changes.

%?? Discuss the most important conclusions before the outline.
We find that the existing RL work for this task \cite{DBLP:journals/eaai/MalialisK15} fails to account for congestion-aware traffic (i.e., TCP, QUIC) and environments with high host density at ingress points.
To remedy this, our agents make throttling decisions per-source, and show how an action model built on domain-specific knowledge can increase performance.
This requires additional engineering: updating RL agents from multiple traces per timestep, smart work scheduling, and an architecture featuring the use of Software-defined Networks (SDN).
Our design minimises the use of (and thus attack surface introduced by) new technologies like SDNs, to increase compatibility with existing infrastructure and simplify operation.
These allow us to demonstrate how much value each feature offers when detecting attack flows.
%In tandem with the development and evaluation of an effective state space and model, we provide the design of a second model inspired by past work on algorithmic DDoS prevention, as an example of the integration of domain-specific knowledge.
This improves substantially upon the state-of-the-art when acting upon most internet traffic (i.e., congestion-aware protocols), and we show that the use of domain knowledge achieves excellent performance at high host density.
Crucially, the models are protocol- and content-agnostic to offer future-proofing against the rollout of future protocols.
%?? Also algorithmic enhancements such as multiple actions per timestep, 
%?? PROTOCOL-AGNOSTIC -- HOW WILL THESE THINGS COPE WITH QUIC ET AL.?!?!
Briefly, this paper contributes:
\begin{itemize}
%	\item A DDoS mitigation system based on direct-control reinforcement learning, designed for deployment in real-world software-defined networks (\cref{sec:environment-and-rl-algorithm,sec:acting-on-individual-sources}).
%	\item Important weaknesses and flaws in the past design and evaluation of similar techniques \cite{DBLP:journals/eaai/MalialisK15}. We offer a deconstruction and empirical study on their formulation, flaws, and risk factors concerning different traffic distributions---in addition, we demonstrate modifications enabling deployment in real-world software-defined networks (\cref{sec:performance-in-an-emulated-environment}).
	\item Two source-level granularity models for RL-driven DDoS prevention (\emph{Instant} and \emph{Guarded} action models) and suitable features (\cref{sec:ddos-mitigation-with-per-flow-reinforcement-learning}).
	\item A description of the system architecture which supports the real-world deployment of such agents (\cref{sec:system-architecture}).
%	\item An investigation of suitable features for this task (\cref{sec:rethinking-the-state-space}).
	\item Reactive simulations of HTTP and VoIP web-server traffic (\cref{sec:a-new-normal}).
	\item A performance comparison of different RL algorithms within these agents, and against the state-of-the-art in RL-based DDoS mitigation (\cref{sec:the-results-of-doing-so}).
%	\item An empirical evaluation of our new models against the state-of-the-art in RL-based DDoS mitigation (\cref{sec:the-results-of-doing-so}).
\end{itemize}

@@

\section{Conclusions}
In this paper we have put forth RL agent designs which act per-flow, describing the algorithmic modifications and engineering choices needed to make their deployment feasible.
Supporting this, we've demonstrated the value of the features these agents use as evidence.
Our evaluation against realistic normal traffic shows that our new agent designs considerably advance the state-of-the-art in RL-based DDoS prevention, protecting \SI{2.5}{$\!\times$} more TCP traffic than past RL work, with \emph{Guarded} agents showing the most promise for future evaluation.

The most direct improvements to be made lie in the correct protection of legitimate UDP traffic, which our agent designs have difficulty safeguarding.
Outside of this, there is scope to test these new techniques against link-flooding attacks in large-scale topologies using reward functions such as \cref{eqn:lfa-reward}.
Simulation is the most likely avenue for such evaluation.
The remaining weaknesses invite many further improvements worth investigation: the design of reward functions derived from QoE metrics, agent operation via \emph{programmable data planes} \cite{DBLP:conf/ancs/JouetP17}, and evaluation against evolving DDoS attacks \cite{DBLP:conf/spw/KangGS16}.

We hope it is clear that RL holds promise and can inspire further innovation.
It allows us to offer distinct advantages above existing works, such as protocol-agnostic DDoS flow detection, more flexible deployment, and automatically learned low-overhead decision-making---without requiring many of the same network resources or capabilities that other techniques discussed in \cref{sec:related-work} rely upon.
Our proposed approach offers substantial improvements for the defence of congestion-aware traffic, which remains the most prevalent class of traffic on the internet today, while offering future-proofing against the introduction of new transports.
It's hoped that more research in this direction will open the door to works which capture the complex and fluid nature of modern networks; evolving topologies, traffic and protocol distributions, and attacks.

>>>>

%?? Discuss the most important conclusions before the outline.
We find that the existing RL work for this task \cite{DBLP:journals/eaai/MalialisK15} fails to account for congestion-aware traffic (i.e., TCP, QUIC) and environments with high host density at ingress points.
To remedy this, our agents make throttling decisions per-source, and show how an action model built on domain-specific knowledge can increase performance.
This requires additional engineering: updating RL agents from multiple traces per timestep, smart work scheduling, and an architecture featuring the use of Software-defined Networks (SDN).
Our design minimises the use of (and thus attack surface introduced by) new technologies like SDNs, to increase compatibility with existing infrastructure and simplify operation.
These allow us to demonstrate how much value each feature offers when detecting attack flows.
%In tandem with the development and evaluation of an effective state space and model, we provide the design of a second model inspired by past work on algorithmic DDoS prevention, as an example of the integration of domain-specific knowledge.
This improves substantially upon the state-of-the-art when acting upon most internet traffic (i.e., congestion-aware protocols), and we show that the use of domain knowledge achieves excellent performance at high host density.
Crucially, the models are protocol- and content-agnostic to offer future-proofing against the rollout of future protocols.
%?? Also algorithmic enhancements such as multiple actions per timestep, 
%?? PROTOCOL-AGNOSTIC -- HOW WILL THESE THINGS COPE WITH QUIC ET AL.?!?!
Briefly, this paper contributes:
\begin{itemize}
	\item Two source-level granularity models for RL-driven DDoS prevention (\emph{Instant} and \emph{Guarded} action models) and suitable features (\cref{sec:ddos-mitigation-with-per-flow-reinforcement-learning}).
	\item A description of the system architecture which supports the real-world deployment of such agents (\cref{sec:system-architecture}).
	\item Reactive simulations of HTTP and VoIP web-server traffic (\cref{sec:a-new-normal}).
	\item A performance comparison of different RL algorithms within these agents, and against the state-of-the-art in RL-based DDoS mitigation (\cref{sec:the-results-of-doing-so}).
\end{itemize}

@@

\section{Conclusions}
In this paper we have put forth RL agent designs which act per-flow, describing the algorithmic modifications and engineering choices needed to make their deployment feasible.
Supporting this, we've demonstrated the value of the features these agents use as evidence.
We've shown that RL algorithms can be modified to suit the learning environment, and how an architecture featuring the (minimal) use of SDNs can aid deployment in diverse networks.
Our evaluation against realistic normal traffic shows that our new agent designs considerably advance the state-of-the-art in RL-based DDoS prevention, protecting \SI{2.5}{$\!\times$} more TCP traffic than past RL work, with \emph{Guarded} agents showing the most promise for future evaluation.

The most direct improvements to be made lie in the correct protection of legitimate UDP traffic, which our agent designs have difficulty safeguarding.
Outside of this, there is scope to test these new techniques against link-flooding attacks in large-scale topologies using reward functions such as \cref{eqn:lfa-reward}.
Simulation is the most likely avenue for such evaluation.
The remaining weaknesses invite many further improvements worth investigation: the design of reward functions derived from QoE metrics, agent operation via \emph{programmable data planes} \cite{DBLP:conf/ancs/JouetP17}, and evaluation against evolving DDoS attacks \cite{DBLP:conf/spw/KangGS16}.
Even now, our approach offers distinct advantages above existing works, such as protocol-agnostic DDoS flow detection, more flexible deployment, and automatically learned low-overhead decision-making on the most prevalent class of traffic.

%We hope it is clear that RL holds promise and can inspire further innovation.
%It allows us to offer distinct advantages above existing works, such as protocol-agnostic DDoS flow detection, more flexible deployment, and automatically learned low-overhead decision-making---without requiring many of the same network resources or capabilities that other techniques discussed in \cref{sec:related-work} rely upon.
%Our proposed approach offers substantial improvements for the defence of congestion-aware traffic, which remains the most prevalent class of traffic on the internet today, while offering future-proofing against the introduction of new transports.
%It's hoped that more research in this direction will open the door to works which capture the complex and fluid nature of modern networks; evolving topologies, traffic and protocol distributions, and attacks.
